\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\setlength{\footskip}{4.08003pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[label={},leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[label={}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://linkedin.com/in/kyletkennedy}{\Large Kyle Kennedy}} & \href{mailto:kylethomaskennedy@gmail.com}{kylethomaskennedy@gmail.com}\\
  \href{https://linkedin.com/in/kyletkennedy}{linkedin.com/in/kyletkennedy} & +1-704-450-1717 \\
  \href{https://github.com/kylekennedy26}{github.com/kylekennedy26} \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Mountain Dev}{Boone, NC}
      {Technical Lead}{November 2025 - Present}
      \resumeItemListStart
        \resumeItem{Full-Stack Development}
          {Built web application for visualizing aerial emissions inspection data using Mapbox, with data export functionality supporting KMZ, Excel, and PDF formats for client reporting.}
        \resumeItem{Architecture}
          {Collaborated with leadership on system design; implemented full stack using FastAPI, Next.js, and PostgreSQL.}
        \resumeItem{Team Leadership}
          {Led team of 3 developers across multiple time zones, coordinating code reviews, sprint planning, and delivery.}

      \resumeItemListEnd

    \resumeSubheading
      {ECR Software Corporation}{Boone, NC}
      {Full-Stack Software Engineer III}{January 2023 - October 2025}
      \resumeItemListStart
        \resumeItem{Career Growth}
          {Promoted twice in under three years, advancing from Junior to Expert based on technical ownership and consistent delivery.}
        \resumeItem{Mobile Development}
          {Led end-to-end mobile app lifecycle as sole engineer for iOS and Android, reducing crash rates by 25\% and ANR rates by 50\% while serving 1,500+ regular users.}
        \resumeItem{Security}
          {Eliminated 90\% of critical vulnerabilities across 5+ applications by implementing NexusIQ and enforcing secure CI/CD pipelines.}
        \resumeItem{Code Quality}
          {Reduced technical debt by 60\% (measured via SonarQube); increased unit test coverage from 0\% to 40\% on legacy Java codebase (300k+ LoC).}
        \resumeItem{Build Optimization}
          {Implemented Maven build optimizations and dependency management improvements, reducing build times by 33\% from 2 hours down to 80 minutes.}
        \resumeItem{Client Engagement}
          {Represented engineering at annual customer conferences, presenting roadmaps and translating client feedback into development priorities.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Appalachian State University}{Boone, NC}
      {Bachelor of Science in Computer Science}{December 2022}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills, Tools, and Technologies}
 \resumeSubHeadingListStart
   \item \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
     \textbf{Languages}{: Java, SQL, Python, TypeScript } \\
     \textbf{Frameworks \& Libraries}{: FastAPI, Next.js, Vue.js, React, GWT } \\
     \textbf{Databases}{: PostgreSQL, SAP SQLAnywhere } \\
     \textbf{Infrastructure \& Cloud}{: Apache Tomcat, GitLab CI/CD, Docker, AWS } \\
     \textbf{Tools}{: Maven, Git, SonarQube, NexusIQ, Gradle, Android Studio, XCode } \\
   \end{tabular*}
 \resumeSubHeadingListEnd

 %-----------AWARDS-----------------
\section{AWARDS}
  \resumeSubHeadingListStart
    \resumeSubItem{ECRS Rookie of the Year Award 2023}
      {Peer-voted award given to the top performing new hire for the year.}
    \resumeSubItem{ECRS Values MVP Award Q2 2023, Q1 2024}
      {Peer-voted award given quarterly to the employee who best exemplifies company values.}
  \resumeSubHeadingListEnd

\end{document}
